---
title: "Homework # 12 ggplot"
author: H24069072
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, fig.align='center')
library(ggplot2)
```

`mpg` is the dataset that comes with ggplot.  You can use `View(mpg)` to get an overview of the dataset. 

1. Using the `mpg` dataset generate a scatter plot of `cty` (city mileage) and `hwy` (highway mileage).

```{r}
data(mpg)
qplot(x=cty,y=hwy,data=mpg, xlab = "City mileage",ylab="Highway mileage")

```


2. Add a colour scale to the scatterplot based on the `displ` variable (engine displacement in liters).

```{r}
data(mpg)
qplot(x=cty,y=hwy,data=mpg, xlab = "The average city mileage",ylab="The average highway mileage", colour = cyl)

```


3. Using the `mpg` dataset recreate the plot as shown below.

```{r}
ggplot(mpg,aes(x=cty,y=hwy,colour=drv))+geom_point()+geom_smooth(method = lm)
```

4. Split the `cty` vs hwy plot into a grid of plots separated by `drv`. 

```{r}
data(mpg)
qplot(x=cty,y=hwy,data=mpg, xlab = "City mileage",ylab="Highway mileage",facets = .~ factor(drv) )

```

5. Generate a boxplot of `cty` comparing `drv` (f=front wheel, r=rear wheel, 4=4 wheel).

```{r}
ggplot(data=mpg, aes(y=cty,x=factor(drv))) + geom_boxplot() +labs(x="drv", y="cty")
```

6. Generate density plots of `hwy` coloured by `drv`.  

```{r}
qplot(hwy, data=mpg, geom ="density", fill=factor(drv), alpha=I(1/2))
```

7. Generate a boxplot of `cty` comparing type of transmission (automatic v.s. manual)

```{r}
qplot(trans,cty, data=mpg, geom =c("boxplot","point","jitter"),xlab ="Transmission")
```

